---
title: "GRIP-APRIL21 @The Sparks Foundation"
author: "Author: Vishal Soni"
subtitle: "TASK 1 : PREDICTION USING SUPERVISIED ML"
output:
  html_notebook: default
  pdf_document: default
---

**DATA SCIENCE AND BUSINESS ANALYTICS. **  
Task- OBJECTIVE: PREDICT THE PERCENTAGE OF AN STUDENT BASED ON THE NUMBER OF STUDY HOURS GIVEN THAT , TO SHOW WHAT WILL BE THE PREDICTED SCORE IF A STUDENT STUDIES FOR 9.25 HRS/DAY?  

**Step-1** Reading the Given Data Set.
```{r}
# Reading The CSV Data

student_data <- read.csv("https://raw.githubusercontent.com/AdiPersonalWorks/Random/master/student_scores%20-%20student_scores.csv", header = TRUE)
head(student_data)
summary(student_data)
```
**Step-2** Plotting the Given Data set.

```{r}
# Plotting the given data

plot(x = student_data$Hours, y = student_data$Scores, xlab = "Hours", ylab = "Scores", main = "Score v/s Hours", col = "blue")
```
**Step-3** Running Linear Regression on the data as there are only Two variables.
```{r}
# Linear regression
student_data_regression <- lm(formula = Scores~Hours, data = student_data)
plot(x = student_data$Hours, y = student_data$Scores, xlab = "Hours", ylab = "Scores", main = "Score v/s Hours", col = "blue")
abline(student_data_regression, col= "Red")

summary(student_data_regression)
```
**Step-4** Splitting Data into Test and Training Data
```{r}
# Splitting Data Into Test and Training data
library(caTools) # package "caTools" is used for splitting the data

split = sample.split(Y = student_data$Scores, SplitRatio = 0.75)
training_set = subset(student_data, split == TRUE)
test_set = subset(student_data, split==FALSE)

training_set # checking the training data
test_set# checking the test data
```
**Step-5** Training the dataset
```{r}
# training 
result <- lm(formula = Scores~Hours, data = training_set)
summary(result)
result$coefficients
```
**Step-6** Using the Test Data to predict the outcome
```{r}
pred <- predict(result, test_set)
head(pred) #printing the predicted result
head(test_set) # printing the head of test set to compare with predicted values
```
**Step-7** Calculating the Mean Absolute Error
```{r}
#taking the head values of original test set
tset <- head(training_set)
tset
# taking the head values of predicted set
pset <- head(test_set)
pset

#Calculating Mean Absolute Error
library(ie2misc)
mae(pset$Hours, tset$Hours)
```
**Step-8** What will be predicted score if a student studies for 9.25 hrs/ day?
```{r}
predicted_result <- predict(result, data.frame(Hours = 9.25))
predicted_result
```
So, the score of student will be **92.40105**.
